### 2008-11-25 doc/sec/ManualofSecurityFramework.tex
Put the user manual away from security technical documentation

\usepackage[spanish,english]{babel}

@@

\hypersetup{pdftex, colorlinks=true, linkcolor=blue, citecolor=blue, filecolor=blue, pagecolor=blue, urlcolor=blue, pdftitle=, pdfauthor=name, pdfsubject=, pdfkeywords=}

@@

\setcounter{secnumdepth}{4}

@@

\renewcommand\theparagraph{\arabic{subsection}.\arabic{subsubsection}.\arabic{paragraph}.}

@@

\newcommand\liststyleWWviiiNumii{%
\newcommand\liststyleWWviiiNumxiii{%
\newcommand\liststyleWWviiiNumxxi{%
\renewcommand\labelitemii{o}
\renewcommand\labelitemiii{[F0A7?]}
\newcommand\liststyleWWviiiNumxvii{%
\renewcommand\labelitemi{o}
\renewcommand\labelitemii{o}
\renewcommand\labelitemiii{[F0A7?]}
\newcommand\liststyleWWviiiNumxix{%
\renewcommand\labelitemi{o}
\newcommand\liststyleWWviiiNumxviii{%
\renewcommand\labelitemi{o}
\renewcommand\labelitemii{o}
\renewcommand\labelitemiii{[F0A7?]}
\newcommand\liststyleWWviiiNumxx{%
\renewcommand\labelitemi{o}
\newcommand\liststyleWWviiiNumxxii{%
\renewcommand\labelitemi{o}
\newcommand\liststyleWWviiiNumxxiii{%
\renewcommand\labelitemi{{}-}
\newcommand\liststyleWWviiiNumiii{%
\renewcommand\theenumi{\alph{enumi}}
\renewcommand\labelenumi{\theenumi)}
\newcommand\liststyleWWviiiNumiv{%
\renewcommand\theenumi{\alph{enumi}}
\renewcommand\labelenumi{\theenumi)}
\newcommand\liststyleWWviiiNumv{%
\renewcommand\theenumi{\alph{enumi}}
\renewcommand\labelenumi{\theenumi)}
\newcommand\liststyleWWviiiNumvi{%
\renewcommand\theenumi{\alph{enumi}}
\renewcommand\labelenumi{\theenumi)}
\newcommand\liststyleWWviiiNumvii{%
\renewcommand\theenumi{\alph{enumi}}
\renewcommand\labelenumi{\theenumi)}
\newcommand\liststyleWWviiiNumviii{%
\renewcommand\labelitemii{[F081?]}
\renewcommand\labelitemiii{${\blacksquare}$}
\renewcommand\labelitemiv{[F06C?]}
\newcommand\liststyleWWviiiNumix{%
\renewcommand\labelitemii{{}-}
\renewcommand\labelitemiii{${\blacksquare}$}
\renewcommand\labelitemiv{[F06C?]}
\newcommand\liststyleWWviiiNumx{%
\renewcommand\labelitemii{[F081?]}
\renewcommand\labelitemiii{${\blacksquare}$}
\renewcommand\labelitemiv{[F06C?]}
\newcommand\liststyleWWviiiNumxiv{%

@@

\newcommand\ps@Convertiv{

@@

\newcounter{Figure}
\renewcommand\theFigure{\arabic{Figure}}

@@

\includegraphics[width=1.4228in,height=0.9098in]{SecurityFrameworkofARC1-img1.jpg}

@@

\begin{flushleft}
\tablehead{}\begin{supertabular}{m{0.83445984in}m{4.78586in}m{0.83655983in}}
\multicolumn{3}{m{6.61436in}}{\raggedleft
\selectlanguage{english}\color{black} NORDUGRID-TECH-16\newline
6/8/08}\\
\multicolumn{3}{m{6.61436in}}{\centering
{\selectlanguage{english}\bfseries\scshape\color{black} Security
Framework of ARC1}\par

~
}\\
\multicolumn{3}{m{6.61436in}}{\centering
\selectlanguage{english}\color{black} W.Qiang, A.Konstantinov}\\
\multicolumn{3}{m{6.61436in}}{\centering
\selectlanguage{english}\itshape\color{black} Abstract}\\
~
 &
\selectlanguage{english}\color{black} This document is about security
design concerns and ideas, as well as security framework implementation
in the ARC1 middleware. &
~
\\
\end{supertabular}
\end{flushleft}
\clearpage{\centering\selectlanguage{english}\bfseries\scshape\color{black}
Table of Contents
\par}

@@

\bigskip
\clearpage\clearpage\setcounter{page}{1}\pagestyle{Convertiv}

@@

\subsection{Introduction}
{\selectlanguage{english}\color{black}
The security framework of the ARC1 includes two parts of capabilities:
security capability embedded in hosting environment, and security
capability implemented as plug-ins with well-defined interfaces which
can be accessed by hosting environment and applications. The following
design concerns were employed when designing:}

\liststyleWWviiiNumii
\begin{itemize}
\item {\selectlanguage{english}\color{black}
Interoperability and standardization}
\end{itemize}
{\selectlanguage{english}\upshape\color{black}
In consistent with the main design concern of the ARC1, interoperability
and standardization is considered in security framework. For example,
in terms of authentication, PKI infrastructure and proxy certificate
(RFC3820 [1]) is used as most of the other grid middle-wares do. Since
supporting of standardization is a way for implementing
interoperability, some standard specifications have been implemented as
prototype and tested, such as SAML specification.}

\liststyleWWviiiNumii
\begin{itemize}
\item {\selectlanguage{english}\color{black}
Modularity and extensibility }
\end{itemize}
{\selectlanguage{english}\upshape\color{black}
Besides the security functionality which is embedded in hosting
environment, the other security functionality is implemented as
plug-ins which has well-defined interfaces, and is configurable and
dynamically loadable. Since the interoperation interface between
security plug-in and hosting environment or applications is predefined,
it is easy to extend the security functionality in order to support
some other security capability by implementing the interface.}

\liststyleWWviiiNumii
\begin{itemize}
\item {\selectlanguage{english}\color{black}
Backward compatibility }
\end{itemize}
{\selectlanguage{english}\color{black}
The GSI (Grid Security Infrastructure) based mechanism has been a
de-facto solution for grid security. The design of security framework
should be compatible to it.}

@@

\subsection{Security architecture in HED. SecHandler and PDP}
\subsubsection{Structure of SecHandler and PDP}
{\selectlanguage{english}\upshape\color{black}
In the implementation of the ARC1, there is a Service Container -- the
Hosting Environment Daemon (HED) (D1.2-2, [2]) which provides a hosting
place for various services in application level, as well as a flexible
and efficient communication mechanism.}

{\selectlanguage{english}\upshape\color{black}
HED contains a framework for implementing and enforcing authentication
and authorization. Each Message Chain Component (MCC) or service has a
common interface for implementing various authentication and
authorization functionality. This functionality is implemented by using
pluggable components (plug-ins) called SecHandler. The SecHandler
components are C++ classes and provide method for processing messages
traveling through Message Chains of the HED. Each MCC or Service
\ usually implement two queues of SecHandlers -- one for incoming
messages and one for outgoing called
{\textquotedblleft}incoming{\textquotedblright} and
{\textquotedblleft}outgoing{\textquotedblright} respectively. It is
possible for MCC or Service to implement other set of queues. Please
check documentation of particular component for that particular
information. All SecHandler components attached to the queue are
executed sequentially. If any of them fails, message processing fails
as well.}

{\selectlanguage{english}\upshape\color{black}
Each SecHandler is configured inside same configuration file used for
configuring whole chain of MCCs. Some of implemented SecHandler
components also make use of pluggable and configurable sub-modules
which specifically handle various security functionalities, such as
authorization, authentication, etc. The currently implemented
sub-modules used by some SecHandlers are Policy Decision Point (PDP)
components such as Arc PDP which can process ARC specific Request and
Policy documents. Figure 1 gives the structure of a MCC/Service, and
the message sequence inside it. And Figure 2 shows the configuration of
SecHandler components for an example
{\textquotedblleft}Echo{\textquotedblright} service.}

\includegraphics[width=5.7709in,height=4.5209in]{SecurityFrameworkofARC1-img2.jpg}

{\selectlanguage{english}\itshape\color{black}
Figure \stepcounter{Figure}{\theFigure}. There are usually two chains of
SecHandlers inside the MCC or service. Each SecHandler will parse the
Security Attributes which are generated by the upstream MCC/services or
probably upstream SecHandlers in the same or other MCC/Service, and do
message processing or authenticate or authorize the incoming/outgoing
message based on the collected information. The SecHandler can also
change the payload and attributes of Messsage itself. For example, the
Username-Token SecHandler will insert the WSS Username Token [3] into
header part of SOAP message. The PDPs are called by the SecHandlers and
are supposed to make authorization decision. Here the two local PDP and
one remote PDP service is just for demonstration, and one or any number
of PDPs can be configured under each SecHandler.}

[Warning: Draw object ignored]

{\centering\selectlanguage{english}\itshape\color{black}
Figure \stepcounter{Figure}{\theFigure}. Example Echo service is
configured to use two SecHandlers, both responsible for authorization.
First SecHandler uses the identity of client extracted from the
incoming message to map it into local identity like local Linux
username. In this case all clients are mapped to local account
{\textquotedblleft}test{\textquotedblright}. The second one uses two
PDPs: one will compose ARC specific authorization request based on the
Security Attributes collected from
{\textquotedblleft}incoming{\textquotedblright} message and evaluate it
against the ARC specific authorization policy which is defined in local
file {\textquotedblleft}policy.xml{\textquotedblright}; the other will
compare the X509 identity of client extracted from the incoming message
against list of identities stored locally.
\par}

\subsubsection{Interface of SecHandler}
{\selectlanguage{english}\upshape\color{black}
When one component (MCC or service) is loaded according to the
configuration information, the SecHandler under the component and the
plug-ins like PDP which are attached to the SecHandler will be loaded
as well. }

{\selectlanguage{english}\upshape\color{black}
There is one simple interface (see Figure 3) defined in class
SecHandler, which will be called by the containing MCC/Service once
there is message (incoming or outgoing) need to be processed.}

{\centering\selectlanguage{english}\itshape\color{black}
Figure \stepcounter{Figure}{\theFigure}. class SecHandler is an abstract
class which includes a general interface called Handle which uses
Message object as argument. Any security handler implementation should
inherit class SecHandler and implement the interface according to the
actual functionality. The interface only return simple Boolean value,
and any useful information generated during the calling of this
interface should be put into the security attribute of the message, or
put into the payload itself. 
\par}

\begin{center}
\begin{minipage}{3.3756in}
{\selectlanguage{english}\color{black}
\ \ class SecHandler \{}

{\selectlanguage{english}\upshape\color{black}
\ \ \ public:}

{\selectlanguage{english}\upshape\color{black}
\ \ \ \ SecHandler(Arc::Config*) \{\};}

{\selectlanguage{english}\upshape\color{black}
\ \ \ \ virtual \~{}SecHandler() \{\};}

{\selectlanguage{english}\upshape\color{black}
\ \ \ \ virtual bool \textit{Handle}(Arc::Message *msg) = 0;}

{\selectlanguage{english}\color{black}
\ \ \};}
\end{minipage}
\end{center}
{\selectlanguage{english}\upshape\color{black}
Currently, the ARC1 comes with the following four security handler
implemented: }

\liststyleWWviiiNumxiii
\begin{itemize}
\item {\selectlanguage{english}\color{black}
\textit{arc.authz} -- Authorization SecHandler}
\end{itemize}
{\selectlanguage{english}\upshape\color{black}
The \textit{arc.authz} is responsible for calling the interface of
policy decision point and getting back the authorization result, and
then making decision according to this authorization result. There is
one simple interface (see Figure 4) defined in PDP, which will be
called by \textit{arc.authz} if configured inside once there is message
(incoming or outgoing) need to be processed.}

\liststyleWWviiiNumxiii
\begin{itemize}
\item {\selectlanguage{english}\color{black}
\textit{identity.map} -- Identity Mapping SecHandler}
\end{itemize}
{\selectlanguage{english}\upshape\color{black}
The \textit{identity.map} is a specific authorization oriented security
handler. It will map the global identity in the message into local
identity like system username based on the result returned by Policy
Decision Point components.}

\liststyleWWviiiNumxiii
\begin{itemize}
\item {\selectlanguage{english}\color{black}
\textit{delegation.collector} -- Delegation SecHandler}
\end{itemize}
{\selectlanguage{english}\upshape\color{black}
The \textit{delegation.collector} is responsible for collecting the
delegation policy information from the remote proxy credential (proxy
certificate is compatible to RFC3820) inside the message, and putting
this policy into message{\textquoteright}s security attribute for the
usage of other components, such as \ \textit{delegation.pdp}.}

\liststyleWWviiiNumxiii
\begin{itemize}
\item {\selectlanguage{english}\color{black}
\textit{usernametoken.handler} -- UseranemToken SecHandler}
\end{itemize}
{\selectlanguage{english}\upshape\color{black}
The task of the \ \textit{usernametoken.handler} is to generate the
WS-Security Username-Token and add it into header of SOAP message which
is the payload of outgoing message. It can also extract the WS-Security
Username-Token from the header of SOAP message which is the payload of
incoming message.}

\subsubsection[Interface of PDP]{Interface of PDP}
\label{bkm:Ref204009855}{\selectlanguage{english}\upshape\color{black}
Figure 4 shows the definition of abstract class PDP. The implementation
could be some function which implements the interface by composing the
policy evaluation request, evaluating this request against some policy,
and returning the evaluation result, or just by composing the policy
evaluation request, invoking some remote policy decision web service
and getting back the evaluation result.}

{\centering\selectlanguage{english}\itshape\color{black}
Figure \stepcounter{Figure}{\theFigure}. class PDP is an abstract class
which includes a general interface called isPermitted which uses
Message object as argument. Any policy decision point implementation
should inherit class PDP and implement the interface according to the
actual functionality. The interface only return simple Boolean value,
and any useful information generated during the calling of this
interface should be put into the security attribute of the message, or
put into the payload itself.
\par}

\begin{center}
\begin{minipage}{3.8756in}
{\selectlanguage{english}\color{black}
\ \ class PDP \{}

{\selectlanguage{english}\upshape\color{black}
\ \ \ public:}

{\selectlanguage{english}\upshape\color{black}
\ \ \ \ PDP(Arc::Config* cfg) \{ \};}

{\selectlanguage{english}\upshape\color{black}
\ \ \ \ virtual \~{}PDP() \{\};}

{\selectlanguage{english}\upshape\color{black}
\ \ \ \ virtual bool \textit{isPermitted}(Arc::Message *msg) = 0;}

{\selectlanguage{english}\color{black}
\ \ \};}
\end{minipage}
\end{center}
{\selectlanguage{english}\upshape\color{black}
Currently, the ARC1 comes with the following four policy decision point
implementation: }

\liststyleWWviiiNumxiii
\begin{itemize}
\item {\selectlanguage{english}\color{black}
\textit{arc.pdp }{}-- Arc PDP}
\end{itemize}
{\selectlanguage{english}\upshape\color{black}
The Arc PDP will organize the security attributes into the ARC specific
authorization request, call the policy evaluator to evaluate the
request against the policy (which is in ARC specific format)
repository, and get back the evaluation result. See paragraph 3 for
detail information about request schema and policy schema.}

\liststyleWWviiiNumxiii
\begin{itemize}
\item {\selectlanguage{english}\color{black}
\textit{delegtion.pdp} -- Delegation PDP}
\end{itemize}
{\selectlanguage{english}\upshape\color{black}
The Delegation PDP is basically similar to Arc PDP, except it uses the
delegation policy parsed from remote proxy credential by
\textit{delegation.collector}, and evaluates the request against
delegation policy. See section 6for the design idea and use case of
delegation policy in fine-grained identity delegation.}

\liststyleWWviiiNumxiii
\begin{itemize}
\item {\selectlanguage{english}\color{black}
\textit{simplelist.pdp} -- Simplelist PDP}
\end{itemize}
{\selectlanguage{english}\upshape\color{black}
The Simplelist PDP is a simplest implementation of policy decision
point. It will match the identity extracted from the remote credential
(or proxy credential) with local list of permitted identities.}

\liststyleWWviiiNumxiii
\begin{itemize}
\item {\selectlanguage{english}\color{black}
\textit{pdpservice.invoker} -- PDP Service Invoker}
\end{itemize}
{\selectlanguage{english}\upshape\color{black}
The PDP Service Invoker is a client which can be used to invoke the PDP
Service which implements the same functionality as Arc PDP, except that
the evaluation request and response are carried by SOAP message. The
benefit of implementing PDP Service and PDP Service Invoker is that the
policy evaluation engine can be accessed remotely and maintained
centrally.}

\subsection[Policy Evaluation Engine]{Policy Evaluation Engine}
\subsubsection{Design of policy evaluation engine}
{\selectlanguage{english}\upshape\color{black}
The ARC1 defines specific evaluation request and policy schema. Based on
the schema definition, one policy evaluation engine is implemented. The
design principal of policy evaluation engine is generality by which the
implementation of the policy evaluation engine can be easily extended
to adopt some other policy schema, such as XACML policy schema.}

{\selectlanguage{english}\upshape\color{black}
Figure 5 shows the UML class diagram about the policy evaluation engine.
It shows all classes and relations simultaneously for getting the
overall picture. }

{\selectlanguage{english}\upshape\color{black}
The \textit{Evaluator} class is the key class for policy evaluation. It
accepts request evaluates it against loaded policy and returns
evaluation response. }

{\selectlanguage{english}\upshape\color{black}
Three abstract factories - \textit{FnFactory}, \textit{AlgFactory},
\textit{AttributeFactory} - are responsible for creating the
\textit{Function}, \textit{CombiningAlg} and \textit{AttributeValue}
objects correspondingly. The classes inherited from
\textit{CombiningAlg} class take care of implementing various combining
algorithms which define relations between
{\textless}Rule/{\textgreater} elements in policy. The
\textit{AttributeValue} type of classes are used for processing
different types of {\textless}Attribute/{\textgreater} and similar
elements. The \textit{Function} classes take care of comparing
{\textless}Attribute/{\textgreater} elements of request and policy. }

{\selectlanguage{english}\upshape\color{black}
The \textit{Policy} class parses {\textless}Policy/{\textgreater} or
{\textless}Rule/{\textgreater} elements and creates
\ \textit{CombingAlg} objects according to the
{\textless}RuleCombiningAlg/{\textgreater} attribute of
{\textless}Policy/{\textgreater}, \textit{Function} objects according
to the {\textless}Function/{\textgreater} attribute of
{\textless}Attribute/{\textgreater} and \textit{AttributeValue} objects
according to the {\textless}Type/{\textgreater} attribute of
{\textless}Attribute/{\textgreater}. Those objects will be used when
evaluating the request.}

{\selectlanguage{english}\upshape\color{black}
The \textit{Request} class is responsible for parsing
{\textless}Request/{\textgreater} element and creates corresponding
\textit{AttributeValue} objects according to the
{\textless}Type/{\textgreater} attribute of
{\textless}Attribute/{\textgreater}. When evaluating, each
\textit{AttributeValue} in request will be evaluated against
corresponding \textit{AttributeValue} in the policy by using relevant
\textit{Function}.}

{\selectlanguage{english}\upshape\color{black}
Due to extensible architecture of code it is relatively easy to add
support for new types of \ \textit{AttributeValue}, \textit{Function
and CombingAlg} objects in this way supporting various types of XML
based policy languages.}

\includegraphics[width=0in,height=0.0161in]{SecurityFrameworkofARC1-img3.png}

\includegraphics[width=0in,height=0.0161in]{SecurityFrameworkofARC1-img4.png}

\includegraphics[width=0in,height=0.0161in]{SecurityFrameworkofARC1-img5.png}

\includegraphics[width=5.7043in,height=5.6354in]{SecurityFrameworkofARC1-img6.png}

{\centering\selectlanguage{english}\itshape\color{black}
Figure \stepcounter{Figure}{\theFigure}. The UML class diagram of the
classes inside policy evaluation engine. 
\par}

\subsubsection{Schemas for policy evaluation engine}
{\selectlanguage{english}\upshape\color{black}
The schema for ARC Policy is available at}

{\selectlanguage{english}\upshape\color{black}
\url{http://svn.nordugrid.org/trac/nordugrid/browser/arc1/trunk/src/hed/pdc/arcpdp/Policy.xsd}
.}

{\selectlanguage{english}\color{black}
The hierarchy tree of ARC Policy is show below (numbers show
multiplicity of elements)}

{\selectlanguage{english}\itshape\color{black}
Policy (1)}

{\selectlanguage{english}\itshape\color{black}
 Rule (1-)}

{\selectlanguage{english}\itshape\color{black}
  Subjects (1)}

{\selectlanguage{english}\itshape\color{black}
   Subject (1-)}

{\selectlanguage{english}\itshape\color{black}
    Attribute (1-)}

{\selectlanguage{english}\itshape\color{black}
   Resources (0-1)}

{\selectlanguage{english}\itshape\color{black}
   Resource (1-)}

{\selectlanguage{english}\itshape\color{black}
  Actions (0-1)}

{\selectlanguage{english}\itshape\color{black}
   Action (1-)}

{\selectlanguage{english}\itshape\color{black}
  Conditions (0-1)}

{\selectlanguage{english}\itshape\color{black}
   Condition (1-)}

{\selectlanguage{english}\itshape\color{black}
    Attribute (1-)}

{\selectlanguage{english}\upshape\color{black}
The schema for ARC Request is available at \ }

{\selectlanguage{english}\upshape\color{black}
\url{http://svn.nordugrid.org/trac/nordugrid/browser/arc1/trunk/src/hed/pdc/arcpdp/Request.xsd}
.}

{\selectlanguage{english}\upshape\color{black}
The hierarchy tree of ARC Request is show below (numbers show
multiplicity of elements)}

{\selectlanguage{english}\itshape\color{black}
Request (1)}

{\selectlanguage{english}\itshape\color{black}
 RequestItem (1-)}

{\selectlanguage{english}\itshape\color{black}
  Subject (1-)}

{\selectlanguage{english}\itshape\color{black}
   SubjectAttribute (1-)}

{\selectlanguage{english}\itshape\color{black}
  Resource (0-)}

{\selectlanguage{english}\itshape\color{black}
  Action (0-)}

{\selectlanguage{english}\itshape\color{black}
  Context (0-)}

{\selectlanguage{english}\itshape\color{black}
   ContextAttribute (1-)}

{\selectlanguage{english}\upshape\color{black}
The schema for ARC Response is available at}

{\selectlanguage{english}\upshape\color{black}
\url{http://svn.nordugrid.org/trac/nordugrid/browser/arc1/trunk/src/hed/pdc/arcpdp/Response.xsd}
.}

{\selectlanguage{english}\upshape\color{black}
The ARC Response is not used directly in code. It is in use by PDP
Service which provides remote evaluation of policies. }

\subsubsection{Basic Elements of Policy}
{\selectlanguage{english}\upshape\color{black}
There are 2 basic objects - {\textquotedbl}policy{\textquotedbl} and
{\textquotedbl}request{\textquotedbl}. There is 1 main actor -
Evaluator. Curretly there are two types of elements in policy: Policy
and Rule. Policy element is made of Rule elements.}

{\color{black}
Evaluator matches request to policy and produces one of 4 following
results:}

\liststyleWWviiiNumxxi
\begin{itemize}
\item {\selectlanguage{english}\color{black}
\textbf{PERMIT} - policy explicitely permits activity specified in
request because request matches some part of policy and corresponding
effect specified in policy is PERMIT. }
\end{itemize}
{\bfseries\itshape\color{black}
Example: }

{\selectlanguage{english}\upshape\color{black}
\textbf{\textit{\ \ \ \ \ \ }}\textbf{\textit{Rule: }}\textit{PERMIT
person ALICE to PLAY in place called WONDERLAND}}

{\selectlanguage{english}\upshape\color{black}
\textbf{\textit{\ \ \ \ \ \ }}\textbf{\textit{Request: }}\textit{person
ALICE wants to PLAY in place called WONDERLAND}}

\liststyleWWviiiNumxxi
\begin{itemize}
\item {\selectlanguage{english}\color{black}
\textbf{DENY} - policy explicitely denies activity specified in Request
because Request matches some part of policy and corresponding effect
specified in policy is DENY.}
\end{itemize}
{\bfseries\itshape\color{black}
Example:}

{\selectlanguage{english}\upshape\color{black}
\textbf{\textit{\ \ \ \ \ \ }}\textbf{\textit{Rule: DENY }}\textit{fruit
APPLE to GROW on PEACH tree}}

{\selectlanguage{english}\upshape\color{black}
\textbf{\textit{\ \ \ \ \ \ }}\textbf{\textit{Request}}\textit{: fruit
APPLE to be GROWN on PEACH tree}}

\liststyleWWviiiNumxxi
\begin{itemize}
\item {\selectlanguage{english}\color{black}
\textbf{INDETERMINATE} - request has some part which does not correspond
to policy.}
\end{itemize}
{\bfseries\itshape\color{black}
Example: }

{\selectlanguage{english}\upshape\color{black}
\textit{\ \ \ \ \ \ }\textbf{\textit{Rule}}\textit{: DENY fruit APPLE to
GROW on PEACH tree}}

{\selectlanguage{english}\upshape\color{black}
\textit{\ \ \ \ \ \ }\textbf{\textit{Request}}\textit{: fruit APPLE to
be GROWN on WHEAT ground}}

{\selectlanguage{english}\upshape\color{black}
\textit{\ \ \ \ \ \ }\textbf{\textit{Request}}\textit{: flower SUNFLOWER
to be grown on PEACH tree}}

{\selectlanguage{english}\upshape\color{black}
\textbf{\textit{Explaination}}: Here, it is not possible to obtain any
matching result - neither positive (DENY or PERMIT) nor negative
(NOT\_APPLICABLE, see below)}

{\color{black}
In the request, the {\textquotedbl}ground{\textquotedbl} is completely
uncomparable to the {\textquotedbl}tree{\textquotedbl} in policy. One
can compare {\textquotedbl}PEACH tree{\textquotedbl} and
{\textquotedbl}APPLE tree{\textquotedbl} because they are both
{\textquotedbl}tree{\textquotedbl}; But it is impossible to compare
{\textquotedbl}PEACH tree{\textquotedbl} and {\textquotedbl}WHEAT
ground{\textquotedbl} becaue they of different kind (Policy is about
tree and Request is about ground).}

{\color{black}
In a similar way one can{\textquotesingle}t compare {\textquotedbl}fruit
APPLE{\textquotedbl} and {\textquotedbl}flower SUNFLOWER{\textquotedbl}
(here policy is about fruits and Request is about flower).}

{\color{black}
Any other situation which makes it impossibile to compare two attributes
will also cause {\textquotedbl}INDETERMINATE{\textquotedbl}.}

\liststyleWWviiiNumxxi
\begin{itemize}
\item {\selectlanguage{english}\color{black}
\textbf{NOT\_APPLICABLE} - all parts of the Request have corresponding
parts in the Policy, but some value of those parts are not the same.
Hence request does not match policy.}
\end{itemize}
{\bfseries\itshape\color{black}
Example:}

{\selectlanguage{english}\upshape\color{black}
\textit{\ \ \ \ \ \ }\textbf{\textit{Rule}}\textit{: DENY fruit APPLE to
GROW on PEACH tree}}

{\selectlanguage{english}\upshape\color{black}
\textit{\ \ \ \ \ \ }\textbf{\textit{Request}}\textit{: fruit APPLE to
be GROWN on APPLE tree }}

{\selectlanguage{english}\upshape\color{black}
\textit{\ \ \ \ \ \ }\textbf{\textit{Request}}\textit{: fruit ORANGE to
be GROWN on PEACH tree }}

{\selectlanguage{english}\upshape\color{black}
\textit{\ \ \ \ \ \ }\textbf{\textit{Request}}\textit{: fruit ORANGE to
be GROWN on APPLE tree }}

{\color{black}
Explanation: for each part of the Request evaluator can find relevant
part in the Policy - both Policy and Request are about fruit and tree.
But the values do not match.}

{\color{black}
If it is required to reduce evaluation results to boolean value PERMIT
maps to TRUE and rest of results to FALSE.}

{\selectlanguage{english}\upshape\color{black}
\textbf{\textit{Note}}\textit{: It would be useful to make it possible
to specify secondary effect which would become }active in case Request
is NOT\_APPLICABLE. For example:}

{\itshape\color{black}
DENY fruit APPLE to GROW on PEACH tree otherwise PERMIT}

{\color{black}
But one should be careful because example above would allow fruit PLUMS
to grow on APPLE trees :)}

{\color{black}
This kind of requirement can be supported by using the algorithm between
policies. \ For example, in case of above scenario, we can use some
algorithm like {\textquotedbl}Permit-if-notapplicable{\textquotedbl}.
See below the {\textquotedbl}Policy matching{\textquotedbl} part for
more explaination. \ }

\subsubsection{Policy MAtching}
{\selectlanguage{english}\upshape\color{black}
Policy is made of Rule elements. Request is evaluated against each Rule.
Each evaluation produces same results as policy evaluation described
above. The results from all Rules are then combined in order to produce
final result for whole policy. Results Combining Algorithm is specified
in Policy. There are 26 algorithms currently:}

\liststyleWWviiiNumxxi
\begin{itemize}
\item {\selectlanguage{english}\color{black}
\textbf{\textit{Deny-Overrides}} - this is default if no algorithm
specified.}

\begin{itemize}
\item {\color{black}
If there is at least one DENY in results final result is DENY.}
\item {\color{black}
Otherwise if there is at least one PERMIT, the final result is PERMIT.}
\item {\color{black}
Otherwise if there is at least one NOT\_APPLICABLE final result is
NOT\_APPLICABLE.}
\item {\color{black}
Otherwise final result is INDETERMINATE.}
\end{itemize}
\end{itemize}
{\selectlanguage{english}\upshape\color{black}
\textbf{NOTE}\textbf{: CHECK if algorithm description is correct}}

{\color{black}
Special case is Policy wih no rules. Probably such policy shoudl be
treated as always producing DENY.}

{\bfseries\color{black}
Discussion}

{\itshape\color{black}
If there is no Rule under Policy, it means no restriction from this
Policy, what exactly shoud the Policy give? DENY or NOT\_APPLICABLE?}

{\itshape\color{black}
It seems to be more logical to produce INDETERMINATE because there is no
rule with elements which could be compared to request.}

\liststyleWWviiiNumxxi
\begin{itemize}
\item {\bfseries\itshape\color{black}
Permit-Overrides.}

\begin{itemize}
\item {\color{black}
If there is at least one PERMIT in results final result is PERMIT.}
\item {\color{black}
Otherwise if there is at least one DENY the final result is DENY.}
\item {\color{black}
Otherwise if there is at least one NOT\_APPLICABLE final result is
NOT\_APPLICABLE.}
\item {\color{black}
Otherwise final result is INDETERMINATE.}
\end{itemize}
\end{itemize}
{\color{black}
Special case is Policy wih no rules. Probably such policy should be
treated as always producing DENY.}

{\bfseries\color{black}
NOTE: CHECK if algorithm description is correct}

{\bfseries\color{black}
Discussion}

{\itshape\color{black}
Question? The same as above.}

\liststyleWWviiiNumxxi
\begin{itemize}
\item {\bfseries\itshape\color{black}
Ordered algorithms.}
\end{itemize}
{\selectlanguage{english}\color{black}
These specify priorities for all four possible results. Their names look
like Result1-Result2-Result3-Result4 with Result\# naming result types,
for example Permit-Deny-NotApplicable-Indeterminate. The results are
combined in following way:}

\liststyleWWviiiNumxxi
\begin{itemize}
\item \begin{itemize}
\item {\color{black}
If there is at least one result of Result1 type then final result is
Result1.}
\item {\color{black}
Otherwise if there is at least one result of Result2 type then final
result is Result2.}
\item {\color{black}
Otherwise if there is at least one result of Result3 type then final
result is Result3.}
\item {\color{black}
Otherwise final result is Result4.}
\end{itemize}
\end{itemize}
{\color{black}
There are 24 possible combinations of those algorithms.}

{\selectlanguage{english}\upshape\color{black}
\textbf{Note:} It would be useful to have more combining algorithms. For
example }

\liststyleWWviiiNumxxi
\begin{itemize}
\item {\selectlanguage{english}\color{black}
Permit-if-notapplicable - the use case could be {\textquotedbl}DENY
fruit APPLE to GROW on PEACH tree otherwise PERMIT{\textquotedbl}. In
this case there is only one Rule under Policy, and this Rule is with
{\textquotedbl}Deny{\textquotedbl} effect. }

\begin{itemize}
\item {\color{black}
If this Rule gives DENY in results, final result is DENY.}
\item {\color{black}
Otherwise if this Rule gives NOT\_APPLICABLE, final result is PERMIT.}
\item {\color{black}
Otherwise final result is INDETERMINATE. }
\end{itemize}
\item {\selectlanguage{english}\color{black}
{\textquotedblleft}Permit-if-allPermit{\textquotedbl} - Permit if all
the Rules gives Permit, this algorithm is useful in case if we are
collecting different policies from a few sources, and we want the
request to satisfy all of them.}

\begin{itemize}
\item {\color{black}
If all of the Rule give PERMIT, the final result is PERMIT.}
\item {\color{black}
Otherwise if there is at least one DENY the final result is DENY.}
\item {\color{black}
Otherwise if there is at least one NOT\_APPLICABLE final result is
NOT\_APPLICABLE.}
\item {\color{black}
Otherwise final result is INDETERMINATE.}
\end{itemize}
\item {\color{black}
OnlyOneApplicable}

\begin{itemize}
\item {\color{black}
If there is one gives INDETERMINATE, final result INDETERMINATE is given
immediately.}
\item {\color{black}
Otherwise if there is exactly only one gives applicable result (DENY or
PERMIT), final result is as this result.}
\item {\color{black}
Otherwise if there is more than one gives applicable result, final
result is INDTERMINATE.}
\item {\selectlanguage{english}\color{black}
Otherwise final result is NOT\_APPLICABLE.}
\end{itemize}
\end{itemize}
{\color{black}
This algorithm makes sure that only one Rule is selected when making
decision.}

\liststyleWWviiiNumxvii
\begin{itemize}
\item {\color{black}
FirstApplicable}

>>>>

\usepackage[english]{babel}

@@

\hypersetup{pdftex, colorlinks=true, linkcolor=blue, citecolor=blue, filecolor=blue, pagecolor=blue, urlcolor=blue, pdftitle=, pdfauthor=qiangwz, pdfsubject=, pdfkeywords=}

@@

\setcounter{secnumdepth}{3}

@@

@@

@@

\newcommand\ps@Convertv{

@@

@@

\includegraphics[width=1.422in,height=0.9091in]{ManualofSecurityFramework-img1.jpg}

@@

\begin{flushleft}
\tablehead{}\begin{supertabular}{m{0.83445984in}m{4.78586in}m{0.83655983in}}
\multicolumn{3}{m{6.61436in}}{\raggedleft
\selectlanguage{english}\color{black} NORDUGRID-TECH-17\newline
15/11/08}\\
\multicolumn{3}{m{6.61436in}}{\centering
{\selectlanguage{english}\bfseries\scshape\color{black} Manual of
Security Framework}\par

~
}\\
\multicolumn{3}{m{6.61436in}}{\centering
\selectlanguage{english}\color{black} W.Qiang, A.Konstantinov}\\
\multicolumn{3}{m{6.61436in}}{\centering
\selectlanguage{english}\itshape\color{black} Abstract}\\
~
 &
\selectlanguage{english}\color{black} This document is about user manual
of security framework, as well as development manual and administration
manual. &
~
\\
\end{supertabular}
\end{flushleft}
\clearpage{\centering\selectlanguage{english}\bfseries\scshape\color{black}
Table of Contents
\par}

@@

@@

\bigskip
\clearpage\clearpage\setcounter{page}{1}\pagestyle{Convertv}

@@

\subsection{1. User Manual}
{\selectlanguage{english}\color{black}
This section describes how to configure and use SecHandler and PDP
elements included in the ARC1 and provides few examples of the ARC
Policy documents. The target readers are those users who will use the
ARC1 middleware. Currently this section is very short on details. It is
going to be continuously extended. Especially taking user feedback into
account.}
